
---
title: 'Simulates assemblages and calculate FD metrics. Supplementary material in: Species and functional diversity accumulate differently in terrestrial mammals'
author: Brunno F. Oliveira^1,2^; Antonin Machac^3,4,5^; Gabriel C. Costa^1^; Thomas M. Brooks^6^; Ana D. Davidson^7^; Carlo Rondinini^8^; Catherine H. Graham^2^;
date: "Global Ecology and Biogeography, 2016 |

**1** Departamento de Ecologia, Universidade Federal do Rio Grande do Norte, Natal, Brasil. |
**2** Department of Ecology and Evolution, Stony Brook University, Stony Brook, New York 11794, USA. |
**3** Center for Macroecology, Evolution, and Climate, Natural History Museum of Denmark, Universitetsparken 15, DK 2100 Copenhagen, Denmark. |
**4** Department of Ecology, Charles University, Vinicna 7, 128 44 Praha 2, Czech Republic. |
**5** Center for Theoretical Study, Charles University and Academy of Sciences of the Czech Republic, Jilska 1, 110 00 Praha 1, Czech Republic. |
**6** International Union for Conservation of Nature, 1196 Gland, Switzerland
7NatureServe, Arlington, VA, USA. |
**8** Global Mammal Assessment Program, Department of Biology and Biotechnologies, Sapienza Universita di Roma, Rome, Italy. |

**Corresponding author:** (brunno.oliveira@me.com)
"
output: pdf_document
theme: united
toc: yes
---

***

>This doccument follows the principles of reproducible research (Peng, 2011). This documment was generated in __R studio__ with `kintr` package. 

*** 

\newpage

1. Packages versions:
===============================
```{r info,message=FALSE,echo=F}
info <- sessionInfo()
```

We used `r info[1]$R$ver` and the following packages:

```{r packages,message=FALSE}
library(FD)
```

```{r echo=F}
setwd("~/Dropbox/Doutorado Brunno/Manuscritos/Chap1 Age and FD/TraitSim/GitHub_repo_simulation_traits")
```

2. Load functions:
=================
```{r runcode}
# modified version of simul_dbFD function from FD packages
source("simul_dbFB_mod.R")

# Pairs correlation
# P-value and r coefficient
panel.cor <- function(x, y, digits=2, cex.cor)
{
  usr <- par("usr"); on.exit(par(usr))
  par(usr = c(0, 1, 0, 1))
  r <- abs(cor(x, y))
  txt <- format(c(r, 0.123456789), digits=digits)[1]
  test <- cor.test(x,y)
  Signif <- ifelse(round(test$p.value,3)<0.001,"p<0.001",paste("p=",round(test$p.value,3)))  
  text(0.5, 0.25, paste("r=",txt))
  text(.5, .75, Signif)
}
# Apply smoth regression line
panel.smooth<-function (x, y, col = "black", bg = NA, pch = 18, 
                        cex = 0.8, col.smooth = "red", span = 2/3, iter = 3, ...) 
{
  points(x, y, pch = pch, col = col, bg = bg, cex = cex)
  ok <- is.finite(x) & is.finite(y)
  if (any(ok)) 
    lines(stats::lowess(x[ok], y[ok], f = span, iter = iter), 
          col = col.smooth, ...)
}
# Add histogram to the diagonal
panel.hist <- function(x, ...)
{
  usr <- par("usr"); on.exit(par(usr))
  par(usr = c(usr[1:2], 0, 1.5) )
  h <- hist(x, plot = FALSE)
  breaks <- h$breaks; nB <- length(breaks)
  y <- h$counts; y <- y/max(y)
  rect(breaks[-nB], 0, breaks[-1], y, col="white", ...)
}
```

3. Simulate assemblages and calculate FD metrics:
=================
3.1 _Experiment 1:_ Simulate trait values following a normal distribution and using parameters extracted from the distribution of body mass observed across mammals   
P.S.: In this first experiment lets use a modified version of the simul.dbFD function from FD package. With this function it is possible to give parameters to generate trait values.   
----------------
```{r simul1, fig.show='hide'}
# s - vector listing the different levels of species richness used in the simulations
# t	- number of traits
# r	- number of replicates per species richness level
# p	- number of species in the common species pool
# tr.method	- character string indicating the sampling distribution for the traits. "unif" is a uniform distribution, "norm" is a normal distribution, and "lnorm" is a lognormal distribution.
# abun.method	- character string indicating the sampling distribution for the species abundances. Same as for tr.method.
# w.abun - logical; should FDis, FEve, FDiv, and Rao's quadratic entropy (Q) be weighted by species abundances?

res1 <- simul.dbFD.mod(s = c(5,10,15,20,25,30,35,40,45,50,55,60,65,70,75,80,85,90,95,100), t = 5, r = 1000, p = 500, tr.par = c(5.05, 2.47), tr.method ="norm", w.abun = F)

results1 <- data.frame(res1$results)
colnames(results1)[1] <- "Richness"
```

3.2 _Experiment 2:_ Simulate trait values following a normal distribution
----------------
```{r simul2, fig.show='hide'}
res2 <- simul.dbFD(s = c(5,10,15,20,25,30,35,40,45,50,55,60,65,70,75,80,85,90,95,100), t = 5, r = 1000, p = 500, tr.method ="norm", w.abun = F)

results2 <- data.frame(res2$results)
colnames(results2)[1] <- "Richness"
```

3.3 _Experiment 3:_ Simulate trait values following a log normal distribution
----------------
```{r simul3, fig.show='hide'}
res3 <- simul.dbFD(s = c(5,10,15,20,25,30,35,40,45,50,55,60,65,70,75,80,85,90,95,100), t = 5, r = 1000, p = 500, tr.method ="norm", w.abun = F)

results3 <- data.frame(res3$results)
colnames(results3)[1] <- "Richness"
```


4. Get standard deviation and range of simulates traits in assemblages:
=================
4.1 _Experiment 1:_
----------------
```{r}
res1$abun[res1$abun > 0] <- 1 

SD <- NA
amp <- NA
for(i in 1:nrow(res1$abun)){
  tmp <- res1$traits[which(res1$abun[i,]==1)]
  SD[i] <- sd(tmp)
  amp[i] <- max(tmp)-min(tmp)
}

experiment1 <- cbind(SD, amp, results1)
```

4.2 _Experiment 2:_
----------------
```{r}
res2$abun[res2$abun > 0] <- 1 

SD <- NA
amp <- NA
for(i in 1:nrow(res2$abun)){
  tmp <- res2$traits[which(res2$abun[i,]==1)]
  SD[i] <- sd(tmp)
  amp[i] <- max(tmp)-min(tmp)
}

experiment2 <- cbind(SD, amp, results2)
```

4.3 _Experiment 3:_
----------------
```{r}
res3$abun[res3$abun > 0] <- 1 

SD <- NA
amp <- NA
for(i in 1:nrow(res3$abun)){
  tmp <- res3$traits[which(res3$abun[i,]==1)]
  SD[i] <- sd(tmp)
  amp[i] <- max(tmp)-min(tmp)
}

experiment3 <- cbind(SD, amp, results3)
```


5. Plot results:
=================
4.1 _Experiment 1:_
----------------
```{r}
pairs(experiment1,
      lower.panel=panel.smooth, upper.panel=panel.cor,diag.panel=panel.hist)
```

4.2 _Experiment 2:_
----------------
```{r}
pairs(experiment2,
      lower.panel=panel.smooth, upper.panel=panel.cor,diag.panel=panel.hist)
```

4.3 _Experiment 3:_
----------------
```{r}
pairs(experiment3,
      lower.panel=panel.smooth, upper.panel=panel.cor,diag.panel=panel.hist)
```


Please cite the original publication.  
Contact brunno.oliveira@me.com for any further information.